Gaps in stellar streams as a result of globular cluster fly-bys

### 2024-11-25 paper/main.tex
added a conclusion

\section{Conclusions}
  \paola{to be written}

>>>>

\section{Conclusions}
  Our study demonstrates that globular cluster flybys can produce density gaps in the stellar streams of clusters like Palomar 5, but the occurrence and characteristics of these gaps depend heavily on the dynamical and structural properties of the stream and the Galactic environment. While our simulations predict the formation of gaps in Palomar 5's tails, the predicted gaps do not align with the regions of the stream currently observed. This discrepancy highlights the challenges in reconciling theoretical predictions with observational data, particularly given the complex interplay between orbital dynamics, stream structure, and the nature of close encounters.

  Several factors contribute to the absence of simulated gaps in the observed portions of Palomar 5's tails, including the stream's varying thickness, the dispersion of action-frequencies near the cluster, and the initial conditions adopted in our simulations. Additionally, the gap creation rates predicted by our model fall short of explaining the number of gaps reported in previous observational studies, suggesting that globular cluster interactions alone cannot fully account for the observed stream substructure.

  Moreover, our results reveal potential tensions with previous numerical studies, such as those by \citet{2019MNRAS.484.2009B}, which found a marginal role for globular clusters in gap formation. This discrepancy may stem from differences in the adopted Galactic potentials, as our analysis suggests that the mass of the dark matter halo in their study may be underestimated, altering the predicted interaction rates.

  The broader implications of our findings indicate that globular cluster interactions add a layer of complexity to interpreting stellar stream substructures, complicating efforts to distinguish between baryonic and dark matter-induced gaps. While Palomar 5's phase-space region may not be ideal for isolating the impact of dark matter subhalos, extending this analysis to other streams, particularly those at larger galactocentric distances, could provide clearer insights.

  Future work should involve a systematic comparison of gap creation rates across various Galactic potentials and extend the scope to a wider range of streams and globular clusters. This would help identify regimes where baryonic and dark matter-induced substructures can be disentangled, shedding light on the elusive influence of dark matter subhalos on stellar streams.
